Spike-and-Slab Generalized Additive Models and Scalable Algorithms for High-Dimensional Data

### 2022-02-25 Manuscript/03-Simulation.Rmd
Revise Variable Selection Results (#22)

\bg{\subsubsection{Variable Selection Performance}
While the main utility of the proposed work is prediction, the proposed model can also serve as variable selection/functional selection as a by-product. Hence We evaluate the variable selection performance. }

>>>>

\bg{\subsubsection{Variable Selection Performance}
Within the simulation settings we examined, the proposed model tends to have a more conservative bebaviour in terms of variable selection, having high precision and low recall. (See Table xxx for gaussian outcomes, and support information xxx for binomial informaitons.) [TODO: mention the variable selection pattern is consistent across the types of outcomes.] THe high precision means that among all the selected variables, high percentage of them are true signals; low recall means that, the model selected small subset among all the positive predictions. Overall, among all the models examined, SB-GAM have the best performance, both high precision and high recall, and yield a high matthew correlation coefficient. Another Bayesian model, spike-and-slab performs bad in terms of variable selection in high-dimensional situations ($p=100,200$). We also want to highlight in our set of linear Gaussian simulations, the SB-GAM performs poorly (See Supproting table 1), while we didn't observe the same for linear binomial outcomes.

}
